Draft - sGBJ

### 2024-12-13 reporting/master_draft/draft_sgbj.qmd
update plot boris comment

```{r upsetplotbreast, fig.cap="Upset plot of the Benjamini-Hockberg p-value agreement according to the different methods", fig.height=10}
ls_plots <- df_breast_cancer_pathway |>
  filter(significant_bh == 1) |>
  group_by(pathway, grade) |>
  summarise(methods = list(unique(as.character(method)))) |>
  group_by(grade) |>
  group_split() |>
  lapply(FUN = function(df_i){
    title_i <- unique(df_i$grade)
    plot_i <- df_i |>
      ggplot(aes(x=methods)) +
      geom_bar() +
      ggupset::scale_x_upset(n_intersections = 6, order_by = "freq") +
      theme_minimal() +
      theme(plot.margin = margin(10, 10, 10, 50)) +
      labs(title = title_i,
           x = "",
           y = "")

@@

plot_pval_breast <- df_breast_cancer_pathway |> 
  filter(p_value != 0) |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method)) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

@@

ggsave(plot_breast,
       filename = here::here("reporting/master_draft/figures/plot_breast.pdf"),
       height = 9,
       width = 7)

@@

```{r upsetplotrembrandt, fig.cap="Upset plot of the Benjamini-Hockberg p-value agreement according to the different methods", fig.height=8}
ls_plots <- df_rembrandt_pathway |>
  filter(significant_bh == 1) |>
  group_by(pathway, grade) |>
  summarise(methods = list(unique(as.character(method)))) |>
  group_by(grade) |>
  group_split() |>
  lapply(FUN = function(df_i){
    title_i <- unique(df_i$grade)
    plot_i <- df_i |>
      ggplot(aes(x=methods)) +
      geom_bar() +
      ggupset::scale_x_upset(n_intersections = 6, order_by = "freq") +
      theme_minimal() +
      theme(plot.margin = margin(10, 10, 10, 50)) +
      labs(title = title_i,
           x = "",
           y = "")

@@

plot_pval_rembrandt <- df_rembrandt_pathway |> 
  filter(p_value != 0) |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method)) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

@@

ggsave(plot_rembrandt,
       filename = here::here("reporting/master_draft/figures/plot_rembrandt.pdf"),
       height = 9,
       width = 7)

>>>>

```{r upsetplotbreast, fig.cap="Upset plot of the Benjamini-Hockberg p-value agreement according to the different methods", fig.height=10}
ls_plots <- df_breast_cancer_pathway |>
  filter(significant_bh == 1) |>
  group_by(pathway, grade) |>
  summarise(methods = list(unique(as.character(method)))) |>
  group_by(grade) |>
  group_split() |>
  lapply(FUN = function(df_i){
    title_i <- unique(df_i$grade)
    plot_i <- df_i |>
      ggplot(aes(x=methods)) +
      geom_bar() +
      ggupset::scale_x_upset(n_intersections = 6, order_by = "freq") +
      theme_minimal() +
      theme(plot.margin = margin(0, 0, 0, 0)) +
      labs(title = title_i,
           x = "",
           y = "")

@@

plot_pval_breast <- df_breast_cancer_pathway |> 
  filter(p_value != 0) |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method), alpha = .4) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

@@

ggsave(plot_breast,
       filename = here::here("reporting/master_draft/figures/plot_breast.pdf"),
       height = 9,
       width = 8)

@@

```{r upsetplotrembrandt, fig.cap="Upset plot of the Benjamini-Hockberg p-value agreement according to the different methods", fig.height=8}
ls_plots <- df_rembrandt_pathway |>
  filter(significant_bh == 1) |>
  group_by(pathway, grade) |>
  summarise(methods = list(unique(as.character(method)))) |>
  group_by(grade) |>
  group_split() |>
  lapply(FUN = function(df_i){
    title_i <- unique(df_i$grade)
    plot_i <- df_i |>
      ggplot(aes(x=methods)) +
      geom_bar() +
      ggupset::scale_x_upset(n_intersections = 6, order_by = "freq") +
      theme_minimal() +
      theme(plot.margin =  margin(0, 0, 0, 0)) +
      labs(title = title_i,
           x = "",
           y = "")

@@

plot_pval_rembrandt <- df_rembrandt_pathway |> 
  filter(p_value != 0) |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method), alpha = .4) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

@@

ggsave(plot_rembrandt,
       filename = here::here("reporting/master_draft/figures/plot_rembrandt.pdf"),
       height = 9,
       width = 8)
